\renewcommand{\refname}{参考文献}	
%
\begin{thebibliography}{55}
\addcontentsline{toc}{chapter}{参考文献}% 追加
%
\bibitem{tb}``3D EXPORT"，最終アクセス：2018年1月22日.
[Online]https://jp.3dexport.com/

\bibitem{tp}``Free3D"，最終アクセス：2018年1月22日.
[Online]http://tf3dm.com/

\bibitem{SQUARE}4Gamer.net，
``［CEDEC 2014］物理シミュレーションの結果に合わせて音を生成する方法とは。スクエニの開発者が語るプロシージャルオーディオの応用例"，最終アクセス：2018年1月22日.\newline
[Online]http://www.4gamer.net/games/032/G003263/20140903036/

\bibitem{Lucas}Bruce D.\,Lucas and Takeo Kanade,
 ``An Iterative Image Registration Technique with an Application to Stereo Vision",
 in \textit{Proceedings of the 7th International Joint Conference on Artificial Intelligence,} No.\,2, pp.\,674--679, 1981.

%\bibitem{CG-ARTS}CG-ARTS，``音を描き出す夢の実現"，最終アクセス：2018年1月22日.\newline
%[Online]https://www.cgarts.or.jp/report/rep\_kr/rep0901.html
%
\bibitem{Bregler}Christoph Bregler, Michele Covell, and Malcolm Slaney,
 ``Video Rewrite Driving Visual Speech with Audio,"
 in \textit{Proceedings of the 24th annual conference on Computer graphics and interactive techniques,} pp.\,353-360, 1997.

\bibitem{james1}Changxi Zheng and Doug L.\,James,
``Harmonic Fluids,"
\textit{ACM Transactions on Graphics,} Vol.\,28, No.\,3, pp.\,37:1-37:12, 2009.

\bibitem{james2}Changxi Zheng and Doug L.\,James,
``Rigid-body Fracture Sound with Precomputed Soundbanks,"
\textit{ACM Transactions on Graphics,} Vol.\,29, No.\,4, pp.\,69:1-69:13, 2010.

\bibitem{facial}Cosker Darren and James Edge,
 ``Laughing, Crying, Sneezing and Yawning:Automatic Voice Driven Animation of Non-Speech Articulations,"
 in \textit{Proceedings of Computer Animation and Social Agents,} pp.\,225-234, 2009.

\bibitem{ue4}Epic Games，``Unreal Engine"，最終アクセス：2018年1月22日.\newline
[Online]https://www.unrealengine.com/ja/what-is-unreal-engine-4

\bibitem{ElKoura}George ElKoura and Karan Singh,
 ``Handrix: Animating the Human Hand,"
  in \textit{Proceedings of the 2003 ACM SIGGRAPH/Eurographics symposium on Computer animation,}
  pp.\,110-119, 2003.

\bibitem{Lee}Hyun-Chul Lee and In-Kwon Lee,
 ``Automatic Synchronization of Background Music and Motion in Computer Animation,"
 \textit{Computer Graphics Forum,} Vol.\,24, No.\,3, pp.\,353-361, 2005.

\bibitem{midi}井上 謙次，``Windows APIによるMIDIプログラミング"，最終アクセス：2018年1月22日.\,
[Online]http://www.deqnotes.net/midi/winapi\_midiprog/winapi\_midiprog.pdf

\bibitem{violin2}Junhwan Kim, Frederic Cordier, and Nadia Magnenat-Thalmann,
 ``Neural Network-based Violinists Hand Animation,"
 in \textit{Proceedings of the 17th Computer Graphics International,} pp.\,37-42, 2000.

\bibitem{violin}Jun Yin, Ankur Dhanik, David Hsu, and Ye Wang,
 ``The Creation of a Music-driven Digital Violinist,"
 in \textit{Proceedings of the 12th Annual ACM International Conference on Multimedia,} pp.\,476-479, 2014.
 
\bibitem{Pauly}Mark Pauly,
 ``Realtime Performance-Based Facial Avatars for Immersive Gameplay," in \textit{Proceedings of Motion on Games,} pp.\,23:23-23:28, 2013.

\bibitem{dance2}二宮　啓，中澤 篤志，竹村 治雄，``音楽に合った舞踊動作の自動生成"，
\textit{Computer Vision and Image Media，} Vol.\,2009，No.\,34，pp.\,1-8，2009.
 
\bibitem{JALI}Pif Edwards, Chris Landreth, Eugene Fiume, and Karan Singh,
 ``JALI An Animator-Centric Viseme Model for Expressive Lip Synchronization,"
 \textit{ACM Transactions on Graphics,} Vol.\,35, No.\,4, pp.\,127:1-127:11, 2016.

\bibitem{DiPaola}Steve DiPaola and Ali Arya,
 ``Emotional Remapping of Music to Facial Animation,"
 in \textit{Proceedings of the 2006 ACM SIGGRAPH symposium on Videogames,} pp.\,143-149, 2006.
  
\bibitem{domino}TAKABO SOFT，``Domino"，最終アクセス：2018年1月22日.\newline
[Online]http://takabosoft.com/domino

\bibitem{sound}Tapio Takala and James Hahn,
 ``Sound Rendering,"
 in \textit{Proceedings of the 19th annual conference on Computer graphics and interactive techniques,} pp.\,211-220, 1992.

\bibitem{Ezzat}Tony Ezzat, Gadi Geiger, and Tomaso Poggio,
 ``Trainable Videorealistic Speech Animation,"
 in \textit{Proceedings of the 29th annual conference on Computer graphics and interactive techniques,} pp.\,388-398, 2002.

\bibitem{dance1}Tae-hoon Kim, Sang Il Park, and Sung Yong Shin,
 ``Rhythmic-Motion Synthesis Based on Motion-Beat Analysis,"
\textit{ACM Transactions on Graphics,} Vol.\,22, No.\,3, pp.\,392-401, 2003.

\bibitem{IFA}Timothy R.\,Langlois and Doug L.\,James,
 ``Inverse-Foley Animation: Synchronizing Rigid-body Motions to Sound,"
 \textit{ACM Transactions on Graphics,} Vol.\,33, No.\,4, pp.\,44:1-44:11, 2014.

\bibitem{Weise}Thibaut Weise, Sofien Bouaziz, Hao Li, and Mark Pauly,
 ``Realtime Performance-Based Facial Animation,"
 \textit{ACM Transactions on Graphics,} Vol.\,30, No.\,4, pp.\,77:1-77:10, 2011.

\bibitem{unity}unity-chan!，最終アクセス：2018年1月22日.
[Online]http://unity-chan.com/

\bibitem{license}unity-chan!，``ユニティちゃんライセンス条項"，最終アクセス：2018年1月22日.\newline
[Online]http://unity-chan.com/contents/license\_jp/

\bibitem{morishima}Wakana Asahina, Narumi Okada, Naoya Iwamoto, Taro Masuda, Tsukasa Fukusato, and Shigeo Morishima,
 ``Automatic Facial Animation Generation System of Dancing Characters Considering Emotion in Dance and Music,"
 in \textit{Proceedings of SIGGRAPH Asia 2015 Posters,} pp.11:1, 2015.

\bibitem{Xu}Yuyu Xu, Andrew W.\, Feng, Stacy Marsella, and Ari Shapiro,
 ``A Practical and Configurable Lip Sync Method for Games,"
 in \textit{Proceedings of Motion on Games,} pp.\,109:131-109:140, 2013.

\bibitem{piano}Yuanfeng Zhu, Ajay Sundar Ramakrishnan, Bernd Hamann, and Michael Neff,
 ``A System for Automatic Animation of Piano Performances,"
  in \textit{Proceedings of Computer Animation and Virtual Worlds,} Vol.\,24, No.\,5, pp.\,445-457, 2012.

\bibitem{Liao}Zicheng Liao, Yizhou Yu, Bingchen Gong, and Lechao Cheng,
 ``Audeosynth: Music-Driven Video Montage,"
 \textit{ACM Transactions on Graphics,} Vol.\,34, No.\,4, pp.\,68:1-68:10, 2015.

\end{thebibliography}